---
title: "Final Project Team BestWish"
author: "Bowie Lam Pui King 3035870595"
date: "2022/2/5"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
setwd(here::here()) ->x
```

## R Markdown
Extract the file, and run the data first
```{r cars}
xlsx_files <- list.files(path = x, pattern="xls")       
library("readxl")
library(pacman)
p_load("tidyverse", "dplyr")
library(stringi)
library(stringr)
library("ggplot2")
library("RColorBrewer")
#install.packages("Polychrome")
library(Polychrome)
library(ggplot2)
library(dplyr)
library(hrbrthemes)
library(babynames)
library(viridis)
p_load("gifski")
install.packages("animation")
library(gapminder)
library(gganimate)
library(gifski)
library(animation)

namesss<-c()
for (i in 1:10){
  assign(str_replace_all(substring(xlsx_files[i],1,str_length(xlsx_files[i])-4),c(" ","-"),c("_","_")), data.frame(read_excel(xlsx_files[i], sheet = "Customised Data Retrieval")))
  namesss<-append(namesss,str_replace_all(substring(xlsx_files[i],1,str_length(xlsx_files[i])-4)," ","_"))
}
```

```{r cars}
#Remember to put ` before and after the data frame name to run the data frame
`Admission_Qualification_of_First-year_Ug_Intakes_by_Age_(hc)`

`Admission_Qualification_of_First-year_Ug_Intakes_by_Institution_(hc)`

`Employment_Situation_of_Full-time_Graduates`           

`First-year_Student_Intakes_(hc)`

`Graduates_(hc)`                       

`Movement_of_Academic_Staff_(fte)`  

`Staff_Number_in_Academic_Departments_(hc)`

`Student_Enrolment_by_Age_(hc)`

`Student_Enrolment_by_Institution_(hc)`

`Students_Who_Discontinued_Their_Studies_(excluding_RPg)_(hc)`
```

```{r cars}
#Question to handle with: (Bowie Lam's part)
# Which industry do most graduates work in? Among different schools, which school contributes the most to different sectors?    
# Graduation situation over the years 
# Employment situation among the high education sector, is the manpower stable among each major? 
# Is the number of students who discontinue their undergraduate increasing?

#Dataset
`Graduates_(hc)` 
`Employment_Situation_of_Full-time_Graduates`
`Staff_Number_in_Academic_Departments_(hc)`
`Students_Who_Discontinued_Their_Studies_(excluding_RPg)_(hc)`

# unique(`Employment_Situation_of_Full-time_Graduates`$Institution)
# `Employment_Situation_of_Full-time_Graduates`
# 
# unique(employmentdf$Occupation)
```

Reporting:
Main Topic: What is going in Higher education sector?
1. IT
2. Employment of Graduation
3. Discontinuation of Students over the year

##Create Plot

Which industry do most graduates work in for full time job? Among different schools?
```{r cars}
# Which industry do most graduates work in for full time job? Among different schools?
`Employment_Situation_of_Full-time_Graduates`%>%
  filter(Level.of.study!="Research postgraduate",Occupation!="Not in Full-time Employment",Occupation!="Workers reporting occupations unidentifiable or inadequately described",Occupation!="Workers not reporting any occupation",Occupation!="Occupations not elsewhere classified") %>%
  select(Academic.Year, Institution,Occupation,No..of.graduates) -> employmentdf

employmentdf$Academic.Year<- str_sub(employmentdf$Academic.Year,1,4)
employmentdf$No..of.graduates<- as.numeric(employmentdf$No..of.graduates)

employmentdf %>%
  group_by(Academic.Year,Institution)%>%
  mutate(
    tot_grad= sum(No..of.graduates)
  ) %>%
  ungroup() ->employmentdf

year<- c("2009","2010","2011","2012","2013")
late_year<- c("2014","2015","2016","2017","2018","2019")

employmentdf %>%
  filter(Academic.Year %in% year)%>%
  group_by(Academic.Year,Institution,Occupation) %>%
  mutate(cate_grad_occu=sum(No..of.graduates),
         percent_count=(cate_grad_occu/tot_grad)*100)-> semploymentdf

semploymentdf[!duplicated(semploymentdf$percent_count), ] -> semploymentdf

getPalette = colorRampPalette(brewer.pal(9, "Set1"))
P30 = createPalette(30,  c("#ff0000", "#00ff00", "#0000ff"))
swatch(P30)
names(P30) <- NULL

#industry_graduates
ggplot(semploymentdf,aes(x = Institution , fill = Occupation, y=cate_grad_occu)) + 
 geom_bar(position = 'fill',stat="identity", color="black")+
  ylab('Proportion accumulated by each occupation')+
  xlab('University (Big 8)')+
  facet_wrap(.~Academic.Year)+
  coord_flip()+
  theme(legend.position="bottom")+
  scale_color_manual(values = P30)+
  labs(title = "Occupation Graduates work with for the past 10 years",
       subtitle = "Among 'Big 8' Universities, differentiated by year")+
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
ggsave("industry_graduates1.png",width = 25, height = 12)
```
Second Garph
```{r car}
late_year<- c("2014","2015","2016","2017","2018","2019")

employmentdf %>%
  filter(Academic.Year %in% late_year)%>%
  group_by(Academic.Year,Institution,Occupation) %>%
  mutate(cate_grad_occu=sum(No..of.graduates),
         percent_count=(cate_grad_occu/tot_grad)*100)-> lemploymentdf

lemploymentdf[!duplicated(lemploymentdf$percent_count), ] -> lemploymentdf

# getPalette = colorRampPalette(brewer.pal(9, "Set1"))
# P30 = createPalette(30,  c("#ff0000", "#00ff00", "#0000ff"))
# swatch(P30)
# names(P30) <- NULL

#industry_graduates
ggplot(lemploymentdf,aes(x = Institution , fill = Occupation, y=cate_grad_occu)) + 
 geom_bar(position = 'fill',stat="identity", color="black")+
  ylab('Proportion accumulated by each occupation')+
  xlab('University (Big 8)')+
  facet_wrap(.~Academic.Year)+
  coord_flip()+
  theme(legend.position="bottom")+
  scale_color_manual(values = P30)+
  labs(title = "Occupation Graduates work with for the past 10 years",
       subtitle = "Among 'Big 8' Universities, differentiated by year")+
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
ggsave("industry_graduates2.png",width = 25, height = 12)


#industry_graduates_gg_animate
ggplot(lemploymentdf,aes(x = Institution , fill = Occupation, y=cate_grad_occu)) +
#ggtitle("Occupation Graduates work with for the past 10 years, Year: ")+
 geom_bar(position = 'fill',stat="identity", color="black")+
  ylab('Proportion accumulated by each occupation')+
  xlab('University (Big 8)')+
  transition_states(Academic.Year) +
  # facet_wrap(.~Academic.Year)+
  coord_flip()+
  theme(legend.position="bottom")+
  scale_color_manual(values = P30)+
  labs(title ="Occupation Graduates work with for the past 10 years, Year: {next_state}")+
  labs(subtitle = "Among 'Big 8' Universities, differentiated by year")+
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))->p_covi
animate(p_covi, nframes = 150, fps = 30, width = 1200, height = 600,renderer = gifski_renderer())
anim_save("another_ind_ani.gif", animation = last_animation())

```
Year by Year Pie chart, Industries distribution among graduates yearly
```{r cars}
#Year by Year Pie chart, Industries distribution among graduates yearly
`Employment_Situation_of_Full-time_Graduates`%>%
  filter(Level.of.study!="Research postgraduate",Occupation!="Not in Full-time Employment",Occupation!="Workers reporting occupations unidentifiable or inadequately described",Occupation!="Workers not reporting any occupation",Occupation!="Occupations not elsewhere classified") %>%
  select(Academic.Year, Institution,Occupation,No..of.graduates) -> total_employ

total_employ$Academic.Year<- str_sub(total_employ$Academic.Year,1,4)
total_employ$No..of.graduates<- as.numeric(total_employ$No..of.graduates)

total_employ %>%
  group_by(Academic.Year,Occupation)%>%
  mutate(aggregate(No..of.graduates, list(Occupation), sum)) %>%
  select(Academic.Year, Occupation, No..of.graduates,x) -> total_employ

colnames(total_employ)[4]<- "Total_grad_by_ind"

total_employ%>%
  group_by(Academic.Year,Occupation)%>%
  distinct(Occupation, .keep_all = TRUE) -> total_employ

total_employ %>%
  group_by(Academic.Year) %>%
  mutate(aggregate(Total_grad_by_ind, list(Academic.Year),sum)) ->new_total_employ

new_total_employ %>%
  select(Academic.Year,Occupation,Total_grad_by_ind,x)->new_total_employ

colnames(new_total_employ)[4]<- "Total_by_year"

#Rank them
new_total_employ%>%
  group_by(Academic.Year)%>%
  mutate(ranking= rank(desc(Total_grad_by_ind)))-> new_total_employ

#now we select only top 10 industries most students work with from each of the year
new_total_employ%>%
  group_by(Academic.Year,Occupation)%>%
  filter(ranking<=10) %>%
  group_by(Academic.Year)%>%
  mutate(
    aggregate(Total_grad_by_ind,list(Academic.Year),sum)
  )%>%
  select(-Group.1)->new_total_employ

colnames(new_total_employ)[6]<- "total_by_rank"
```


Make the graph now
```{r cars}
# Compute percentages
new_total_employ$fraction <- new_total_employ$Total_grad_by_ind / new_total_employ$total_by_rank

# Compute the cumulative percentages (top of each rectangle)
new_total_employ$ymax <- cumsum(new_total_employ$fraction)

# Compute the bottom of each rectangle
new_total_employ$ymin <- c(0, head(new_total_employ$ymax, n=-1))

# Compute label position
new_total_employ$labelPosition <-(new_total_employ$ymax + new_total_employ$ymin) / 2

# Compute a good label
new_total_employ$label <- paste0(new_total_employ$Occupation, "\n", round((new_total_employ$fraction)*100,2), "%")

cp <- coord_polar(theta = "y")
cp$is_free <- function() TRUE

year<- c("2009","2010","2011","2012")
late_year<- c("2013","2014","2015","2016")
late_yearr<-c("2018","2019")

new_total_employ%>%
  filter(Academic.Year %in% year) ->cnew_total_employ

new_total_employ%>%
  filter(Academic.Year %in% late_year) ->dnew_total_employ

new_total_employ%>%
  filter(Academic.Year %in% late_yearr) ->enew_total_employ

# Make the plot
ggplot(new_total_employ, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=Occupation)) +
  geom_rect() +
  scale_fill_brewer(palette = 'Paired') +
  geom_label(x=4, aes(y=labelPosition, label=label), size=1.5)  +
  facet_wrap(~Academic.Year, scale = 'free', ncol = 4)+
  cp+
  xlim(c(2,4)) +
  theme(aspect.ratio = 1)+
  theme(legend.position = "right")+
  labs(title = "Industries Graduates participated",
       subtitle = "Over the last ten years")+
  ylab("Filter by Top Ten Occupation per year")+
   theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank(),
        plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
# ggsave("Pie_chart_yearbyyear.png",width = 25, height = 12)

#Gif for many years-------------------------------------------------------------------------------------------------------------
# p_load("gifski")
# install.packages("animation")
# library(gapminder)
# library(gganimate)
# library(gifski)
# library(animation)
library(animation)
saveGIF({
  for (i in unique(new_total_employ$Academic.Year)) {
    p = ggplot(new_total_employ[new_total_employ$Academic.Year== i,], aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=Occupation,frame=Academic.Year)) +
  # transition_states(Academic.Year) +
  geom_rect() +
  scale_fill_brewer(palette = 'Paired') +
  geom_label(x=4, aes(y=labelPosition, label=label), size=3)  +
  facet_wrap(~Academic.Year, scale = 'free')+
  cp+
  xlim(c(2,4)) +
  theme(aspect.ratio = 1)+
  theme(legend.position = "none")+
  labs(title = "Industries Graduates participated",
       subtitle = "Over the last ten years")+
  ylab("Filter by Top Ten Occupation per year")+
   theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank(),
        plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
    print(p)
  }
}, movie.name="ind_grad_gf.gif")
```

Split Graph
```{r car}
ggplot(cnew_total_employ, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=Occupation)) +
  geom_rect() +
  scale_fill_brewer(palette = 'Paired') +
  geom_label(x=4, aes(y=labelPosition, label=label), size=3)  +
  facet_wrap(~Academic.Year, scale = 'free', ncol = 2)+
  cp+
  xlim(c(2,4)) +
  theme(aspect.ratio = 1)+
  theme(legend.position = "right")+
  labs(title = "Industries Graduates participated",
       subtitle = "Over the last ten years")+
  ylab("Filter by Top Ten Occupation per year")+
   theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank(),
        plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
ggsave("Pie_chart_yearbyyear1.png",width = 25, height = 12)

ggplot(dnew_total_employ, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=Occupation)) +
  geom_rect() +
  scale_fill_brewer(palette = 'Paired') +
  geom_label(x=4, aes(y=labelPosition, label=label), size=3)  +
  facet_wrap(~Academic.Year, scale = 'free', ncol = 2)+
  cp+
  xlim(c(2,4)) +
  theme(aspect.ratio = 1)+
  theme(legend.position = "right")+
  labs(title = "Industries Graduates participated",
       subtitle = "Over the last ten years")+
  ylab("Filter by Top Ten Occupation per year")+
   theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank(),
        plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
ggsave("Pie_chart_yearbyyear2.png",width = 25, height = 12)

ggplot(enew_total_employ, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=Occupation)) +
  geom_rect() +
  scale_fill_brewer(palette = 'Paired') +
  geom_label(x=4, aes(y=labelPosition, label=label), size=3)  +
  facet_wrap(~Academic.Year, scale = 'free', ncol = 2)+
  cp+
  xlim(c(2,4)) +
  theme(aspect.ratio = 1)+
  theme(legend.position = "right")+
  labs(title = "Industries Graduates participated",
       subtitle = "Over the last ten years")+
  ylab("Filter by Top Ten Occupation per year")+
   theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank(),
        plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
ggsave("Pie_chart_yearbyyear3.png",width = 25, height = 12)

```

Percentage Change Graph
```{r car}
total_employ %>%
  group_by(Occupation) %>%
  mutate(pct_change=(Total_grad_by_ind/lag(Total_grad_by_ind)-1)*100) -> total_employ_pct

total_employ_pct[is.na(total_employ_pct)] <- 0

total_employ_pct

# Libraries
# library(ggplot2)
# library(babynames) # provide the dataset: a dataframe called babynames
# library(dplyr)
# library(hrbrthemes)
# library(viridis)

# Keep only 3 names
don <- babynames %>% 
  filter(name %in% c("Ashley", "Patricia", "Helen")) %>%
  filter(sex=="F")
  
# Plot
n<- 27
# library("RColorBrewer")
# #install.packages("Polychrome")
# library(Polychrome)
unique(total_employ_pct$Occupation)
oo<- c("Accountants and Auditors","Architects and Surveyors",                     
"Artists"    ,                                   "Business Professionals"  ,                     
"Clerical and Related Workers",                  "Economists, Statisticians and Mathematicians" ,
 "Engineering Technicians"      ,                 "Engineers"                                  ,  
  "Other Professionals and Technical Workers")

ooo<- c( "Production and Related Workers"    ,           
 "Religious Workers"                             ,"System Analysts and Computer Programmers"     ,
 "Legal Workers"                                 ,"Agriculture and Fishery Workers"     ,         
"Aircraft and Ship Officers"                    ,"Authors, Journalists and Related Writers"    , 
 "Government Officials (General Grades)" )

oooo<-c("Insurance, Real Estate, and Business Services",
 "Managers"                                      ,"Medical and Health Workers"    ,               
 "Other Service Workers"                         ,"Physical and Life Science Technicians"      ,  
 "Physical and Life Scientists"                  ,"Protective Service Workers"  ,                 
 "Sales/Service Workers"                         ,"Teaching Profession"    ,                      
 "Government Administrators and Diplomats")



total_employ_pct %>%
  filter(Occupation %in% oo) %>%
  ggplot(aes(x=Academic.Year, y=pct_change, group=Occupation, color=Occupation)) +
  scale_color_viridis(discrete = TRUE)+
    geom_line(size=2) +
    scale_color_viridis(discrete = TRUE) +
    ggtitle("Percentage Change of Graduate partipation Year over Year") +
    theme_bw() +
  theme(legend.position = "none")+ylab("Percentage Change (%)")+xlab("Academic Year")+
    facet_wrap(.~Occupation, scales = "free",  ncol = 3)
ggsave("pct_change_ind_1.png",width = 25, height = 12)

total_employ_pct %>%
  filter(Occupation %in% ooo) %>%
  ggplot(aes(x=Academic.Year, y=pct_change, group=Occupation, color=Occupation)) +
  scale_color_viridis(discrete = TRUE)+
    geom_line(size=2) +
    scale_color_viridis(discrete = TRUE) +
    ggtitle("Percentage Change of Graduate partipation Year over Year") +
    theme_bw() +
  theme(legend.position = "none")+ylab("Percentage Change (%)")+xlab("Academic Year")+
    facet_wrap(.~Occupation, scales = "free",  ncol = 3)
ggsave("pct_change_ind_2.png",width = 25, height = 12)

total_employ_pct %>%
  filter(Occupation %in% oooo) %>%
  ggplot(aes(x=Academic.Year, y=pct_change, group=Occupation, color=Occupation)) +
  scale_color_viridis(discrete = TRUE)+
    geom_line(size=2) +
    scale_color_viridis(discrete = TRUE) +
    ggtitle("Percentage Change of Graduate partipation Year over Year") +
    theme_bw() +
  theme(legend.position = "none")+ylab("Percentage Change (%)")+xlab("Academic Year")+
    facet_wrap(.~Occupation, scales = "free",  ncol = 3)
ggsave("pct_change_ind_3.png",width = 25, height = 12)

total_employ_pct %>%
  ggplot(aes(x=Academic.Year, y=pct_change, group=Occupation, color=Occupation)) +
  scale_color_viridis(discrete = TRUE)+
    geom_line(size=2) +
    scale_color_viridis(discrete = TRUE) +
    ggtitle("Percentage Change of Graduate partipation Year over Year") +
    theme_bw() +
  theme(legend.position = "none")+ylab("Percentage Change (%) (Standardised)")+xlab("Academic Year")+
    facet_wrap(.~Occupation,ncol = 6)
ggsave("tot_pct_change_ind.png",width = 25, height = 12)
```

```{r cars}
total_employ_pct %>%
  filter(Occupation == "System Analysts and Computer Programmers") -> it_indust

# Plot
ggplot(it_indust, aes(x=Academic.Year, y=Total_grad_by_ind)) +
  geom_segment(
    aes(x=Academic.Year, xend=Academic.Year, y=0, yend=Total_grad_by_ind), 
    color=ifelse(it_indust$Academic.Year == "2019" | it_indust$Academic.Year == "2015", "red", "grey"), 
    size=ifelse(it_indust$Academic.Year == "2019"|it_indust$Academic.Year =="2015", 1.3, 0.7),
  ) +
  geom_point(
    color=ifelse(it_indust$Academic.Year == "2019" |it_indust$Academic.Year == "2015", "red", "grey"), 
    size=ifelse(it_indust$Academic.Year == "2019" | it_indust$Academic.Year =="2015", 5, 2),
  ) +
  theme_bw() +
  coord_flip(ylim = c(0,2000),expand = TRUE) +
  theme(
    legend.position="none"
  ) +
  xlab("Year") +
  ylab("Number of Students") +
  ggtitle("Number of Graduates working in IT industries, by year")+
# Add annotation
 annotate("text", x=grep("2019", it_indust$Academic.Year), y=it_indust$Total_grad_by_ind[which(it_indust$Academic.Year=="2019")]*1.2, 
           label="Highest number of students: 923 ", 
           color="red", size=4.5 , angle=0, fontface="bold", hjust=0) + 
  
    annotate("text", x=grep("2015", it_indust$Academic.Year), y=it_indust$Total_grad_by_ind[which(it_indust$Academic.Year=="2015")]*1.2, 
           label = paste("The year in which the Technology Bureau was initatiated: ",it_indust$Total_grad_by_ind[which(it_indust$Academic.Year=="2015")] %>% round(2)) , 
           color="red", size=4.5 , angle=0, fontface="bold", hjust=0)
ggsave("lollipop_IT.png",width = 15, height = 24)
```



Among the big 5 industries, where are those employees come from?
```{r cars}
#Among the big 5 industries, which university has most of their employees studied from?
`Employment_Situation_of_Full-time_Graduates`%>%
  filter(Level.of.study!="Research postgraduate",Occupation!="Not in Full-time Employment",Occupation!="Workers reporting occupations unidentifiable or inadequately described",Occupation!="Workers not reporting any occupation",Occupation!="Occupations not elsewhere classified") %>%
  select(Academic.Year, Institution,Occupation,No..of.graduates) -> employmentdf

employmentdf$Academic.Year<- str_sub(employmentdf$Academic.Year,1,4)
employmentdf$No..of.graduates<- as.numeric(employmentdf$No..of.graduates)

employmentdf %>%
  group_by(Academic.Year,Institution,Occupation)%>%
  mutate(
    tot_grad_cate= as.numeric(aggregate(No..of.graduates,list(Occupation), sum)[2])
  ) -> df1

df1 %>%
  group_by(Academic.Year,Occupation) %>%
  mutate(
    tot_cate_sum = sum(No..of.graduates)
  ) %>%
  select(-No..of.graduates)-> df1
#remove duplicated value within Occupation
df1%>%
  group_by(Academic.Year, Institution) %>%
  distinct(Occupation, .keep_all= TRUE) -> df1
#Include proportion column
df1 %>%
  group_by(Academic.Year, Occupation)%>%
  mutate(proportion= tot_grad_cate/tot_cate_sum) -> df1

big_five_industries<- c("Accountants and Auditors","Business Professionals","Engineers","Medical and Health Workers","System Analysts and Computer Programmers")

year<- c("2017","2018","2019")

df1 %>%
  filter(Occupation %in% big_five_industries) -> df1

ggplot(df1, aes(fill=Institution, y=tot_grad_cate, x=Academic.Year)) + 
  geom_bar(position="fill", stat="identity")+
    geom_text(
    aes(label = round(proportion*100,2)),
    colour = "white", size = 3,
    vjust = 1.5, position = position_fill(.9)
  )+
  ylab("Proportion accumulated by each Institution")+xlab("Academic Year")+
  facet_wrap(.~Occupation)
ggsave("big_5_proportions.png",width = 25, height = 12)


# #emp_cate_gg_animate
# ggplot(lemploymentdf,aes(x = Institution , fill = Occupation, y=cate_grad_occu)) +
# #ggtitle("Occupation Graduates work with for the past 10 years, Year: ")+
#  geom_bar(position = 'fill',stat="identity", color="black")+
#   ylab('Proportion accumulated by each occupation')+
#   xlab('University (Big 8)')+
#   transition_states(Academic.Year) +
#   # facet_wrap(.~Academic.Year)+
#   coord_flip()+
#   theme(legend.position="bottom")+
#   scale_color_manual(values = P30)+
#   labs(title ="Occupation Graduates work with for the past 10 years, Year: {next_state}")+
#   labs(subtitle = "Among 'Big 8' Universities, differentiated by year")+
#   theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))->p_covi
# animate(p_covi, nframes = 150, fps = 50, width = 1200, height = 600,renderer = gifski_renderer())
# anim_save("another_ind_ani.gif", animation = last_animation())


ggplot(df1, aes(fill=Institution, y=tot_grad_cate, x=Academic.Year)) + 
  geom_bar(position="fill", stat="identity")+
  transition_states(Occupation) +
    geom_text(
    aes(label = round(proportion*100,2)),
    colour = "white", size = 3,
    vjust = 1.5, position = position_fill(.9)
  )+
  labs(title ="Where do our graduates come from? Occupation: {next_state}")+
  ylab("Proportion accumulated by each Institution")+xlab("Academic Year")-> p_covi2
animate(p_covi2, nframes = 150, fps = 30, width = 1200, height = 600,renderer = gifski_renderer())
anim_save("grad_empl.gif", animation = last_animation())
```


Is the number of students who discontinue their undergraduate studies increasing? 
Which School has the most student discontinuing recently?
```{r cars}
`Students_Who_Discontinued_Their_Studies_(excluding_RPg)_(hc)` %>%
  select(-Mode.of.study)-> df_discontinue

df_discontinue$Academic.Year<- str_sub(df_discontinue$Academic.Year,1,4)

colnames(df_discontinue)[4]<- "Discontinued_number"
df_discontinue$Discontinued_number<- as.numeric(df_discontinue$Discontinued_number)


df_discontinue %>%
  group_by(Academic.Year,Institution,Level.of.study)%>%
  filter(Academic.Year!="2009")%>%
  mutate(
    tot_dis= as.numeric(aggregate(Discontinued_number,list(Level.of.study), sum)[2])
  ) %>%
  distinct(tot_dis, .keep_all = TRUE) %>%
  select(-Discontinued_number) ->df_discontinue
```

```{r cars}
#Graph
ggplot(df_discontinue, aes(x=Academic.Year, y=tot_dis, group=Level.of.study)) + 
  ylab("Quantity") + 
  facet_wrap(.~Institution)+
  geom_line(aes(linetype = Level.of.study, color=Level.of.study), size=2) + 
  geom_point(aes(color = Level.of.study), size=5) + 
  geom_label(
    aes(label=tot_dis), 
    nudge_x = 0.25, nudge_y = 0.25, 
    check_overlap = T
  )+
  labs(title = "Number of Students that discontinue their studies",
       subtitle = "Situation among different schools for last ten years")+
  scale_linetype_manual(values=c("solid", "solid","solid")) + 
  scale_color_manual(values=c('#DC143C','#4169E1',"#11f276")) + 
  theme_grey() +
  theme(legend.position = "right")+ylab("Number of Students")+xlab("Academic Year")+
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
ggsave("students_discontinue.png",width = 25, height = 12)
```

Overall Trend of HK students discontinuing their studies
```{r cars}
`Students_Who_Discontinued_Their_Studies_(excluding_RPg)_(hc)` %>%
  select(-Mode.of.study)-> total_discontinue

total_discontinue$Academic.Year<- str_sub(total_discontinue$Academic.Year,1,4)

colnames(total_discontinue)[4]<- "Discontinued_number"
total_discontinue$Discontinued_number<- as.numeric(total_discontinue$Discontinued_number)

total_discontinue%>%
  group_by(Academic.Year)%>%
  mutate(
    aggregate(Discontinued_number,list(Academic.Year), sum)
  ) %>%
  select(Academic.Year,x) ->total_discontinue

colnames(total_discontinue)[2]<- "Total_Students_discontinue"

total_discontinue%>%
  filter(Academic.Year!="2009")%>%
  distinct(Academic.Year, .keep_all = TRUE) -> total_discontinue

ggplot(total_discontinue, aes(x=Academic.Year, y=Total_Students_discontinue,fill=as.factor(Academic.Year))) + 
  geom_bar(stat = "identity") + scale_color_brewer(palette="RdYIBu") +
  theme(legend.position="None")+
  geom_text(aes(label = Total_Students_discontinue), vjust = 1.5)+
  ylab("Total number of Students discontinued")+
  xlab("Academic Year")+
  labs(title = "Total Number of Students that discontinue their studies",
       subtitle = "From 'Big 8' Universities")+
  theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))
ggsave("Total_discontinue_trend.png",width = 25, height = 12)
```
